Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Proof-of-Concept VI}}

### 2014-12-02 Paper.tex
More spec for CALLCODE.

0xf2 & {\small RETURN} & 2 & 0 & Halt execution returning output data. \\

>>>>

0xf2 & {\small CALLCODE} & 7 & 1 & Message-call into this account with alternative account's code. \\
&&&& Same as CALL to this account, except that the code is exchanged for $\boldsymbol{\sigma}[\boldsymbol{\mu}_s[1]]_c$. \\
0xf3 & {\small RETURN} & 2 & 0 & Halt execution returning output data. \\
